Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-07 VegOzone.tex
Fix typo and move figure

\begin{figure*}[t]
  %\includegraphics[width=12cm]{ozone_timeseries_fenoscandic_obs.png}
  \includegraphics[width=12cm]{fig04}
  \caption{Time series of ozone observations in northern Fennoscandia (Tab.~\ref{tab:ebas_obs}) (1986--2019). Data from EBAS until December 2018. The hatched areas indicate periods with insufficient quality control according to \citet{NILU2003}. (a) Esrange (SWE); (b) Pallas (FIN); (c) Jergul/Karasjok; (d) Svanvik; (e) Janiskoski.}
  \label{fig:ozone_timesseries_fenoscandic_obs}
\end{figure*}

\section{Statistical analysis}
\label{sec:stats}
In this section, we assess the climate conditions and multi-annual mean (referred to as climatology in thhe following) annual cycle of gound-level ozone concentrations at Svanhovd. To this end, we derive climatologies for temperature, precipitation, global irradiance, and ozone. We evaluate statistical significance of divergances from the norm in these variables for the growing seasons 2018/19 (referred to as anomalies). We perform a bias correction on the Svanvik ozone climatology with respect to long-term series of \chem{[O_3]} at the sites in northern Finland and Sweden.

@@

We found representative ozone climatologies (multi-annual means) for northern Fennoscandia and Svanhovd based on ground-level ozone monitoring. To account for missing data from our 2018 record, we proposed a routine for gap filling of ozone observations following a Reynolds's decomposition into anomalies and climatology. In the course, we also assessed the quality of available global (MACC and CAMS) and regional (CAMS Regional Air Quality (CAMSRAQ) ensemble) reanalysis products for Europe concerning ozone. We have studied the ozone seasonality for northern Fennoscandia and the quality of its representation in available global and regional reanalysis products for Europe. We confirm that both global reanalysis products do not reproduce the observed ozone patterns in northern Fennoscandia \citep{GMD:Huijnen2020,ACPD:Barten2020}. Only the CAMSRAQ ensemble reproduces the observed ozone seasonality, although with a remaining low-bias. This confirms that high spatial resolution and assimilation of in situ observations of ground-level ozone concentrations are a must to constrain reanalysis products related to air quality and risk assessment ozone damage to vegetation, especially in high latitudes.

>>>>

\section{Statistical analysis}
\label{sec:stats}
In this section, we assess the climate conditions and multi-annual mean (referred to as climatology in the following) annual cycle of gound-level ozone concentrations at Svanhovd. To this end, we derive climatologies for temperature, precipitation, global irradiance, and ozone. We evaluate statistical significance of divergances from the norm in these variables for the growing seasons 2018/19 (referred to as anomalies). We perform a bias correction on the Svanvik ozone climatology with respect to long-term series of \chem{[O_3]} at the sites in northern Finland and Sweden.

@@
